
\documentclass[a4paper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\namesection{Luke}{Cooper}{ % Your name
\urlstyle{same}\url{https://www.linkedin.com/in/luke-cooper-a60790167/} \\ % Your website, LinkedIn profile or other web address
\href{mailto:lukecoopz@gmail.com}{lukecoopz@gmail.com} | (+64) 0278158673 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Auckland University}

\descript{Bachelor of Science}
Majoring in Computer Science and Information Systems.

\location{Grad. Sept 2018 | Auckland, NZ}

\sectionspace % Some whitespace after the section

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Undergraduate}

\location{Computer Science}
Operating Systems \\
Discrete Structures in Mathematics \\
Functional Programming \\
Programming Techniques \\
Introduction to Software Development \\
Human Computer Interaction \\
Image Processing \\
Modern Data Communications \\

\sectionspace % Some whitespace after the section

\location{Information Systems}
Business Systems Analysis \\
Database Systems \\
Data Communications and the Internet \\
ERP SAP Introduction \\

\sectionspace

%------------------------------------------------
% Links
%------------------------------------------------

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\smallspace % Some whitespace after the section
C\# \textbullet{} Cypress \textbullet{} Python \textbullet{} HTML \\
\smallspace % Some whitespace after the section
SQL \textbullet{} Playwright \textbullet{} CSS \textbullet{} \LaTeX\ \\
\smallspace % Some whitespace after the section
JavaScript \textbullet{} TypeScript\\
\smallspace
Test Automation \textbullet{} QA Testing \\ 
\smallspace
Selenium \textbullet{} CI/CD 


\sectionspace % Some whitespace after the section
\sectionspace % Some whitespace after the section

\section{Referees} 
\textbf{Brenton Wong} \\
Engineering Manager \\
Vacasa \\
021 399 304 \\
brenton.f.wong@gmail.com \\
\smallspace
\smallspace\smallspace
\textbf{Campbell Moss} \\
Director of Engineering \\ 
Vacasa \\
027 654 6555 \\
campbell.moss@gmail.com\\


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Dronedeploy}
\descript{| QA Cloud Engineer}

\location{June 2024 - Current | NZ}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item As a QA Cloud Engineer on the Robotics team at DroneDeploy, I established QA practices from the ground up, implementing and maintaining CI/CD pipelines to support automated testing, release management, and quality reporting. I design and maintain automation frameworks using Playwright with TypeScript, and contribute test coverage for the rocos-agent in Go. I also oversee testing across multiple microservices, ensuring reliability, scalability, and smooth production release cycles. 

\end{tightitemize}
\sectionspace % Some whitespace after the section

\runsubsection{Vacasa}
\descript{| Senior QA Engineer}

\location{Aug 2021 - June 2024 | NZ}
\begin{tightitemize}
\item I am a QA Engineer with expertise in implementing test practices, creating automation tests, and documenting test plans. I focus on increasing test coverage by developing automated tests, reducing manual testing workload for the team. My coding skills in Typescript allow me to create tests using Cypress and integrate them into the CI/CD pipeline. I oversee testing activities for two repositories: one for API and another for front-end web application testing. \linebreak Additionally, I train new QA engineers, ensuring they are proficient in our company's tools and familiar with effective testing methodologies.

\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{Datacom}
\descript{| Test Analyst}

\location{Sept 2019 – Aug 2021 | Auckland, NZ}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Conducted thorough QA testing for newly developed features, diligently documenting comprehensive testing strategies. Utilized C\# and Selenium to create automation test cases tailored to the newly implemented functionalities, and enhancing both regression and smoke tests.\linebreak

\end{tightitemize}



\runsubsection{Dimension Data}
\descript{| Migration Engineer \linebreak (Fletcher Building Contract)}

\location{Sept 2018 – Sept 2019 | Auckland, NZ}

\begin{tightitemize}
\item Windows 7 to Windows 10 Migration for approx 6000 machines throughout New Zealand. Also including standardisation of all business units under all Fletcher Building Subsidiaries and collaboration of all domains. I worked closely with office managers, staff and back-end engineers to ensure a smooth and trouble-free migration.
\end{tightitemize}
%------------------------------------------------
% Research
%------------------------------------------------
\section{Projects}
\runsubsection{Homelab}
\descript{}
\location{June 2024 - Present}\begin{tightitemize}
\item In my spare time, I enjoy building and maintaining my homelab, where I run a variety of self-hosted applications. This has given me experience with Docker containers, system administration, and troubleshooting, while deepening my understanding of infrastructure and deployment workflows.
\end{tightitemize}

\sectionspace % Some whitespace after the section
\runsubsection{Raspberry Pi }
\descript{}

\location{Jan 2022 – March 2024}\begin{tightitemize}
\item I managed to get my hands on a Rasberry Pi 3 and have been playing around with this in my spare time. Tinkering around with small projects like PiHole, Local network share, Plex media server, VPN etc.  
\end{tightitemize}
\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column
\end{document}